An HPSG account for verbal reduplication in Mandarin Chinese

### 2023-06-08 chapters/ch01-Intro.tex
Update 2023-06-08-18:56:45

In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning (e.g. \citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
    in the example sentences will be set in italics.}
Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while”.

>>>>

In Mandarin Chinese, verbs can be reduplicated to express a delimitative aspectual meaning (e.g. \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
This means that the event or state denoted by the verb happens in a short duration and/or a low frequency \citep[155]{XiaoMcEnery2004}, such as illustrated in (\ref{ex:redup-ex}).\footnote{Reduplications
    in the example sentences will be set in italics.}
Thus, verbal reduplication in Mandarin Chinese is often translated as doing something ``a little bit/for a little while”.

### 2023-06-08 chapters/ch02-Phenomenon.tex
Update 2023-06-08-18:56:45

The reduplication has a \textit{delimitativeness} meaning (e.g. \citealt[204--205]{Chao1968}; \citealt[29]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
Besides delimitativeness, \citet{Chao1968}, \citet{Fan1964}, \citet{Li1996}, \citet{Smith1991, Smith1994} and \citet{Tsao2001} suggested that the reduplication signifies \textit{tentativeness}, which can be used
``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet{Fan1964}, \citet{Li1996} and \citet{Qian2000} as the meaning of reduplication, as well.
 \citet{Fan1964} further proposed a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
 \citet{Zhu1998} suggested that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.

@@

The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
\citet{Chao1968}, \citet{LiThompson1981} and \citet{Liao2014} listed reduplication under morphological processes. 
\citet{Arcodiaetal2014}, \citet{Xiong2016}, \citet{BascianoMelloni2017}, \citet{YangWei2017}, \citet{MelloniBasciano2018}, \citet{Xie2020},   on the other hand, claimed it to be syntactic.
%And e.g. \citet{Chen2001}, \citet{Chen2005}  and \citet{Yang2003} did not make any claim about its grammatical status.
This section reviews the arguments in \citet{Xie2020}, applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
and compares the behaviors of the reduplication with those of Parallel Verb Compounds 
(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
The results argue for a morphological status of reduplication.

@@

However, a morphological process can be productive, and it does not necessarily change the category or valency of the input.
For instance, the \textit{-bar} derivation in German is a productive morphological process \citep[381]{Mueller2013}. 
The \textit{be-} prefixation in German does not change the category of the input: \textit{arbeiten} `work' $\rightarrow$ \textit{bearbeiten} `handle'. 
And inflections of tense in German do not change the valency of the input verb.
Further, if \textit{le} is considered to be a morphological element \citep[e.g.][]{Huangetal2009, MuellerLipenkova2013}, the insertion of \textit{le} does not have to be viewed as a syntactic
process either.
It seems that \citet{Xie2020} only showed that AA and ABAB are different processes than AABB, but not necessarily that the former is syntactic while the latter morphological.

@@

The first syntactic test is phrasal extension, namely the addition of optional elements \citetext{\citealp[150]{Duanmu1998}; \citealp[280]{Schaefer2009}}. 
Optional elements that can possibly appear in a phrase should be able to be added into it,
and subparts of a phrase should be able to be modified separately. 
If the unit is a word, however, then neither of these should  be possible.
As illustrated in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) in \sectref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet{Huangetal2009} and \citet{MuellerLipenkova2013} considered aspect markers in Mandarin Chinese to be morphological elements. E.g. \citet{Travis2000, Arcodiaetal2014, BascianoMelloni2017} considered aspect information to be syntactically encoded.} 
And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).
Turning to separate modification,  the element in the reduplication cannot be modified individually. 
Compared to (\ref{ex:ext-redup1}), where the adverbial \textit{qingsheng de} `quietly' modifies the whole reduplication, (\ref{ex:ext-redup2}) is ungrammatical, 
as the adverbial cannot modify the second element in the reduplication alone.
It is worth mentioning that in (\ref{ex:ext-redup1}), it is not possible to analyze \textit{qingsheng de} `quietly' to modify only the first element in the reduplication, 
because the adverbial does not necessarily occur adjacent to the verb, as in (\ref{ex:ext-redup3}), 
and it still modifies the whole predicate.
(\ref{ex:ext-redup1}) and  (\ref{ex:ext-redup3}) have the same meaning.

>>>>

The reduplication has a \textit{delimitativeness} meaning (e.g. \citealt[204--205]{Chao1968}; \citealt[232]{LiThompson1981};  \citealt[14]{Li1996}; \citealt[70]{Dai1997};  \citealt[382--383]{Zhu1998}; \citealt[420--421]{Xing2000}; \citealt[48]{Chen2001};  \citealt[288]{Tsao2001}; \citealt[11--12]{Yang2003}; \citealt[Sec. 4.3]{XiaoMcEnery2004}). 
To be specific, the reduplication of [$+$durative] verbs reduces the duration of the events,
and the reduplication of [$-$durative] verbs reduces the iteration frequency of the events \citetext{\citealp[14]{Li1996}; \citealp[149--150]{XiaoMcEnery2004}}.
Besides delimitativeness, \citet{Chao1968}, \citet{Fan1964}, \citet{Li1996}, \citet{Smith1991, Smith1994} and \citet{Tsao2001} suggested that the reduplication signifies \textit{tentativeness}, which can be used
``to refer modestly to one's own activities, or for mild imperatives'' \citep[356]{Smith1991}, or ``trying to'' do something \citep[234]{LiThompson1981}.
\textit{Frequentativeness} or \textit{habitualness}, that the event denoted by the verb happens frequently or habitually, is mentioned by \citet{Fan1964}, \citet{Li1996} and \citet{Qian2000} as the meaning of reduplication, as well.
 \citet{Fan1964} further proposed a meaning of \textit{slightness} or \textit{casualness} for reduplication, which implies that the event is unimportant or conveys a casual attitude of the speaker.
 \citet{Zhu1998} suggested that the main function of reduplication is to \textit{increase the agency} of the action or the change denoted by the verb.

@@

The literature on reduplication makes different assumptions on whether it is a morphological or syntactic phenomenon.
\citet[Ch. 4]{Chao1968}, \citet[Ch. 3]{LiThompson1981} and \citet[4--5]{Liao2014} listed reduplication under morphological processes. 
\citet{Arcodiaetal2014}, \citet{Xiong2016}, \citet{BascianoMelloni2017}, \citet{YangWei2017}, \citet{MelloniBasciano2018}, \citet{Xie2020},   on the other hand, claimed it to be syntactic.
%And e.g. \citet{Chen2001}, \citet{Chen2005}  and \citet{Yang2003} did not make any claim about its grammatical status.
This section reviews the arguments in \citet{Xie2020}, applies the tests proposed by \citet{Duanmu1998} and \citet{Schaefer2009} to distinguish words from phrases in Mandarin Chinese 
and compares the behaviors of the reduplication with those of Parallel Verb Compounds 
(compounds which consist of two verbs that ``either are synonymous or signal the same type of predicative notions'' \citep[68]{LiThompson1981}, e.g. \textit{gou-mai} `purchase-buy, buy') and {SVC}s. 
The results argue for a morphological status of reduplication.

@@

However, a morphological process can be productive, and it does not necessarily change the category or valency of the input.
For instance, the \textit{-bar} derivation in German is a productive morphological process \citep[330]{Mueller2002}. 
The \textit{be-} prefixation in German does not change the category of the input: \textit{arbeiten} `work' $\rightarrow$ \textit{bearbeiten} `handle'. 
And inflections of tense in German do not change the valency of the input verb.
Further, if \textit{le} is considered to be a morphological element (e.g. \citealt[101--102]{Huangetal2009}; \citealt[246]{MuellerLipenkova2013}), the insertion of \textit{le} does not have to be viewed as a syntactic
process either.
It seems that \citet{Xie2020} only showed that AA and ABAB are different processes than AABB, but not necessarily that the former is syntactic while the latter morphological.

@@

The first syntactic test is phrasal extension, namely the addition of optional elements \citetext{\citealp[150]{Duanmu1998}; \citealp[280]{Schaefer2009}}. 
Optional elements that can possibly appear in a phrase should be able to be added into it,
and subparts of a phrase should be able to be modified separately. 
If the unit is a word, however, then neither of these should  be possible.
As illustrated in (\ref{ex:forms-mono})--(\ref{ex:forms-vo}) in \sectref{sec:forms}, the reduplication can only be separated by \textit{le} and \textit{yi}. 
As mentioned above, whether aspect markers are considered to be morphological or syntactic elements depends on the theoretical framework (and possibly the target language).\footnote{For example, \citet[Sec. 3.3.1]{Huangetal2009} and \citet[246]{MuellerLipenkova2013} considered the postverbal aspect markers (\textit{-le}, \textit{-zhe} and \textit{-guo}) in Mandarin Chinese to be morphological elements. E.g. \citet{Travis2000, Arcodiaetal2014, BascianoMelloni2017} considered all aspect information to be syntactically encoded.} 
And the status of \textit{yi} is unclear, since it does not carry any additional meaning or grammatical function in the structure. % (more on this topic see Section \ref{sec:jackendoff}).
Turning to separate modification,  the element in the reduplication cannot be modified individually. 
Compared to (\ref{ex:ext-redup1}), where the adverbial \textit{qingsheng de} `quietly' modifies the whole reduplication, (\ref{ex:ext-redup2}) is ungrammatical, 
as the adverbial cannot modify the second element in the reduplication alone.
It is worth mentioning that in (\ref{ex:ext-redup1}), it is not possible to analyze \textit{qingsheng de} `quietly' to modify only the first element in the reduplication, 
because the adverbial does not necessarily occur adjacent to the verb, as in (\ref{ex:ext-redup3}), 
and it still modifies the whole predicate.
(\ref{ex:ext-redup1}) and  (\ref{ex:ext-redup3}) have the same meaning.

### 2023-06-08 chapters/ch04-Previous.tex
Update 2023-06-08-18:56:45

\citet{Fan1964}, \citet{Chao1968} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet{Chao1968} or \textit{cognate object} in \citet{Chao1968, Hong1999}.
The \textit{verbal classifier phrase}  is also termed \textit{quantity adverbial} in \citet{LiThompson1981} or \textit{frequency phrase} in \citet{Huangetal2009}.}.
A verbal classifier is ``a measure for verbs of action expresses the number of times an action takes place” \citep[615]{Chao1968}, such as the \textit{ci} in (\ref{ex:clf}).

@@

 \citet{YangWei2017} endorsed the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.

\citet{Tsai2008} provided the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
He observed that  \textit{zhe} `\textsc{prog}', \textit{le} `\textsc{pfv}' and \textit{wan} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}), 
while \textit{zai} `\textsc{dur}' and \textit{guo} `\textsc{exp}' can occur without further information (\ref{ex:complete}).

>>>>

\citet{Fan1964}, \citet{Chao1968} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet[615]{Chao1968} or \textit{cognate object} in \citet[312]{Chao1968} and  \citet[263]{Hong1999}.
The \textit{verbal classifier phrase}  is also termed \textit{quantity adverbial} in \citet[352--353]{LiThompson1981} or \textit{frequency phrase} in \citet[91]{Huangetal2009}.}.
A verbal classifier is ``a measure for verbs of action expresses the number of times an action takes place” \citep[615]{Chao1968}, such as the \textit{ci} in (\ref{ex:clf}).

@@

 \citet{YangWei2017} endorsed the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
 \citet{Tsai2008} provided the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
He observed that  \textit{zhe} `\textsc{prog}', \textit{le} `\textsc{pfv}' and \textit{wan} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}), 
while \textit{zai} `\textsc{dur}' and \textit{guo} `\textsc{exp}' can occur without further information (\ref{ex:complete}).
